\LARGE \bf Experimental Validation of Reference Spreading for Robotic Manipulation of Unmodeled Objects

### 2022-11-30 PaperPreliminary.tex
b

    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}

    \input{bibconfig.tex}

@@

    A logistical aspect where machines struggle to fully compete with humans is object manipulation. A practical examples of this is depalletizing. While robots are strong and consistent when manipulating objects, humans are versatile and swift. Robots are held back from faster performance because they must often slow down prior to making contact; establishing contact at a high velocity -- an event referred to as an impact -- could cause damage to the robot or its environment. On the contrary, humans intrinsically exploit impacts in the form of grabbing, bouncing and hitting. (give better explanation of depalletizing: manual and automatic approach)

@@

    Reference spreading can also handle simultaneous impacts. \cite{vansteenRobotControlSimultaneous2021} (explanation)

@@

    \textbf{(4. Intermediate impact phase controller:)}

@@

    (image of robots)

@@

    \section{Soft end effector design}

    \subsection{Base controller}
    For articulated robot arms, it is convenient to control the end effector in Cartesian space, rather than directly controlling the robot's joints. In the case of the 7-DoF Franke Emika robot, this leaves one redundant DoF however. Furthermore, despite the desire to control the end effector Carthesian space,

    This can be accomplished with an impedance controller.

@@

    Stiffness $K$ is typically chosen as a diagonal matrix. The damping matrix is determined following $D = 2(\Lambda K)^{\frac{1}{2}}$ which guarantees stable behavior when $K$ and $\Lambda$ are symmetric. Furthermore, For the inertia matrix, two options were considered. Choosing a diagonal matrix $\Lambda$ decouples the accelerations w.r.t. to the position error, resulting in better tracking in free motion. This approach was used in~\cite{vanoorschotDesignNumericalValidation2022}. In this work, however, the task-space inertia is set to match the joint-space inertia following $\Lambda^{-1} = JM^{-1}J^T$, decoupling the contact force w.r.t. the position error for better performance during contact. Further motivation for this decision is provided in Appendix xxx. % = \begin{bmatrix} e_{rotation} & e_{translation} \end{bmatrix}^T $.

@@

    \begin{table}[h]
    \label{target_defs}
      \caption{Impedance target definition}{Definition of the targets $p_t$, $\dot{p}_t$, and $F_t$ during the different impact phases. Multiple options for the intermediate phase are considered.}

      \centering
    \begin{tabular}{ccc|cccc|}
    \cline{4-7}
                                      &                                    &               & \multicolumn{4}{c|}{Intermediate}                                              \\ \cline{2-7} 
    \multicolumn{1}{c|}{}             & \multicolumn{1}{c|}{Ante}          & Post          & 0             & 1         & 2             & 3                                  \\ \hline
    \multicolumn{1}{|c|}{$p_t$}       & \multicolumn{1}{c|}{$p^a_r$}       & $p^p_r$       & $p^p_r$       & $p^a_r$   & $p^a_r$       & $\gamma p^a_r+(1-\gamma)p^p_r$     \\
    \multicolumn{1}{|c|}{$\dot{p}_t$} & \multicolumn{1}{c|}{$\dot{p}^a_r$} & $\dot{p}^p_r$ & $\dot{p}^p_r$ & $\dot{p}$ & $0$ & $\gamma p + (1-\gamma)\dot{p}^p_r$ \\
    \multicolumn{1}{|c|}{$F_t$}       & \multicolumn{1}{c|}{$F^a_r$}       & $F^p_r$       & $F^p_r$       & $F^a_r$   & $F^a_r$       & $\gamma F^a_r + (1-\gamma)F^p_r$   \\ \hline
    \end{tabular}
    \end{table}
% % Section
%     \section{Controller}
%     Impedance controller passes the following task-space acceleration to the QP scheme:
%     $$\ddot{p}_t = \ddot{p}_d + \Lambda^{-1}F_{imp}$$
%     with 
%     $$F_{imp} =  K(p_d-p_t)+D (\dot{p}_d-\dot{p}_t) +F_{ref} $$
%     during the ante- or post impact phase. During the intermediate impact phase, this $F_{imp}$ is changed to 
%     $$F_{imp} =  K(p_d-p_t)+ \gamma [ D (\dot{p}_d-\dot{p}_t) +F_{ref}] $$
%     with $$\gamma = \frac{ t_{impact}-t_{current}}{T_{intermediate}}.$$ Once $\gamma \leq 1$, intermidate impact mode is switched to post-impact mode is enabled.

>>>>

    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{xcolor}
    \input{bibconfig.tex}

@@

    A logistical aspect where machines struggle to fully compete with humans is object manipulation. A practical examples of this is depalletizing. While robots are strong and consistent when manipulating objects, humans are versatile and swift. Robots are held back from faster performance because they must often slow down prior to making contact; establishing contact at a high velocity -- an event referred to as an impact -- could cause damage to the robot or its environment. On the contrary, humans intrinsically exploit impacts in the form of grabbing, bouncing and hitting. \textcolor{red}{(give better explanation of depalletizing: manual and automatic approach)}

@@

    Reference spreading can also handle simultaneous impacts. \cite{vansteenRobotControlSimultaneous2021} \textcolor{red}{(explanation)}

@@

    \textbf{\textcolor{red}{(4. Intermediate impact phase controller:)}}

@@

    \textcolor{red}{(image of robots)}

@@

\subsection{Task description}
Describe the environment, e.g. weigth and dimension of boxes. Then explain what the robot should do with the environment during the experiment: stamp the table, grab boxes, and the possibility for more complex movements such as pivotting a box. (Pivotting a box is not a good usecase for evaluating reference spreading however.)
    \section{Soft end effector design}
    \section{Trajectory planning using teleoperation}
    \subsection{VR device}
    \subsection{Impedance controller}
    For articulated robot arms, it is convenient to control the end effector in Cartesian space, rather than directly controlling the robot's joints. This can be accomplished with an impedance controller.

@@

    Stiffness $K$ is typically chosen as a diagonal matrix. The damping matrix is determined following $D = 2(\Lambda K)^{\frac{1}{2}}$ which guarantees stable behavior when $K$ and $\Lambda$ are symmetric \textcolor{red}{ref?}. Furthermore, For the inertia matrix, two options were considered. Choosing a diagonal matrix $\Lambda$ decouples the accelerations w.r.t. to the position error, resulting in better tracking in free motion. This approach was used in~\cite{vanoorschotDesignNumericalValidation2022}. In this work, however, the task-space inertia is set to match the joint-space inertia following $\Lambda^{-1} = JM^{-1}J^T$, decoupling the contact force w.r.t. the position error for better performance during contact. Further motivation for this decision is provided in Appendix xxx. % = \begin{bmatrix} e_{rotation} & e_{translation} \end{bmatrix}^T $.

@@

    \begin{table}[h]
      \caption{Impedance target definition}{Definition of the targets $p_t$, $\dot{p}_t$, and $F_t$ during the different impact phases. Multiple options for the intermediate phase are considered.}

    \label{target_defs}
      \centering
    \begin{tabular}{ccc|cccc|}
    \cline{4-7}
                                      &                                    &               & \multicolumn{4}{c|}{Intermediate}                                              \\ \cline{2-7} 
    \multicolumn{1}{c|}{}             & \multicolumn{1}{c|}{Ante}          & Post          & 0             & 1         & 2             & 3                                  \\ \hline
    \multicolumn{1}{|c|}{$p_t$}       & \multicolumn{1}{c|}{$p^a_r$}       & $p^p_r$       & $p^p_r$       & $p^a_r$   & $p^a_r$       & $\gamma p^a_r+(1-\gamma)p^p_r$     \\
    \multicolumn{1}{|c|}{$\dot{p}_t$} & \multicolumn{1}{c|}{$\dot{p}^a_r$} & $\dot{p}^p_r$ & $\dot{p}^p_r$ & $\dot{p}$ & $0$ & $\gamma p + (1-\gamma)\dot{p}^p_r$ \\
    \multicolumn{1}{|c|}{$F_t$}       & \multicolumn{1}{c|}{$F^a_r$}       & $F^p_r$       & $F^p_r$       & $F^a_r$   & $F^a_r$       & $\gamma F^a_r + (1-\gamma)F^p_r$   \\ \hline
    \end{tabular}
    \end{table}

    \section{Results}
    Show results of stamping and grabbing task between: no RS and RS with various intermediate modes. For the figures, only show the relevant directions, e.g. downward direction for stamping task.

    \section{Conclusion}

    \section{Future work}

    \section{Appendix}
    \begin{itemize}
    \item Full manufacturing process of end effector with pictures
    \item Full technical drawings of end effector

    \item Additional plots for stamping and grabbing experiment (in main text, only show relevant direction, e.g. downward direction for stamping task)
    \item Definition of the rotation error. Could also be a reference to someone else rather than an eppendix entry.

    \end{itemize}
% % Section
%     \section{Controller}
%     Impedance controller passes the following task-space acceleration to the QP scheme:
%     $$\ddot{p}_t = \ddot{p}_d + \Lambda^{-1}F_{imp}$$
%     with 
%     $$F_{imp} =  K(p_d-p_t)+D (\dot{p}_d-\dot{p}_t) +F_{ref} $$
%     during the ante- or post impact phase. During the intermediate impact phase, this $F_{imp}$ is changed to 
%     $$F_{imp} =  K(p_d-p_t)+ \gamma [ D (\dot{p}_d-\dot{p}_t) +F_{ref}] $$
%     with $$\gamma = \frac{ t_{impact}-t_{current}}{T_{intermediate}}.$$ Once $\gamma \leq 1$, intermidate impact mode is switched to post-impact mode is enabled.
